Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-07-01 Replication/Results/data_analysis/preproc/Analysis_exp7_prepro.rmd
raincloud plot

# check the number of trials are correct
excldSub1_M  <- c()     # subject ID of those who failed matching task
excldSub1_C  <- c(7338) # subject 7338 excluded because Accuracy of one condition is zero

df.M1.trials <-  plyr::ddply(df.M1,.(Subject, Match, Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC))
subjlistM <- unique(df.M1.trials$Subject)
excldSub2_M <- c()
for (ii in 1:length(subjlistM)){
  tmp <- subset(df.M1.trials,Subject == subjlistM[ii])
  if(sum(tmp$N != 75)){ # if the number of trials in matching task correct 
    excldSub2_M[ii] <- subjlistM[ii]
    print(paste0("ERROR: the trials number of subject ", subjlistM[ii] , 
                 " in matching task is not correct"))
}}

@@

# df.M1 <- df.M1[!(df.M1$Subject %in% procFailureSub),]
# df.C1 <- df.C1[!(df.C1$Subject %in% procFailureSub),]

# calculate the overall accuracy for matching task
df.M1.acc.g <-  plyr::ddply(df.M1,.(Subject), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

@@

excldSub_M   <- c(excldSub1_M, excldSub2_M,excldSub3_M)
excldSub_M <- excldSub_M[!duplicated(excldSub_M)]   # total excluded for matching task

@@

valdSub_M <- setdiff(subjlistM, excldSub_M)
valdSub_C <- setdiff(subjlistC, excldSub_C)

# select valid data for further analysis

df.M1.valid <- df.M1[!(df.M1$Subject %in% excldSub_M),]   # exclude the invalid subjects
df.C1.valid <- df.C1[!(df.C1$Subject %in% excldSub_C),]
# df.C1.valid <- df.C1.valid[!(df.C1.valid$Subject %in% excld.sub.T),]

@@

# get the data file for hddm analysis

df.M.ddm.v <- df.M[!(df.M$Subject %in% excldSub_M),]   # exclude the invalid subjects
df.C.ddm.v <- df.C[!(df.C$Subject %in% excldSub_C),]

@@

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.M1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Good")
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
RTdata2 <- df.M1.V.sum_rt_acc_l %>%
  select(Subject,Match,Morality,Identity,RT) %>% 
  filter(Match == "match" & Morality == "Bad")
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")

setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
Ddata1 <- df.M1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Good")
Ddata1$Identity <- factor(Ddata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = Ddata1, aes(y = dprime, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,4))+labs(x = "Good",y = "dprime")
Ddata2 <- df.M1.V.SDT_l %>%
  select(Subject,Morality,Identity,dprime) %>% 
  filter(Morality == "Bad")
Ddata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = Ddata2, aes(y = dprime, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = dprime,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,4),breaks = NULL)+labs(x = "Bad",y = "")
p_dprime_match <- multiplot(p1,p2,cols = 2)
# ggsave("p_rt_match.pdf", p_rt_match, scale = 1,height = 6, width = 8, dpi = 300, family = "Times")
setwd(traDir)
tiff("p_dprime_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_dprime_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
#multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")

ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Val"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = ACCdata2, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1),breaks = NULL)+labs(x = "Bad",y = "")
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
ACCdata1 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Good')
ACCdata1$Identity <- factor(ACCdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = ACCdata1, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1))+labs(x = "Good",y = "Accuracy")
ACCdata2 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,ACC) %>% 
  filter(Task == "Id"& Morality == 'Bad')
ACCdata2$Identity <- factor(ACCdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = ACCdata2, aes(y = ACC, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = ACC,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(0,1),breaks = NULL)+labs(x = "Bad",y = "")
setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
RTdata2 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Val"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")

setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
RTdata1 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Good')
RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
                    #+ coord_cartesian(ylim=c(300,900))

#y_scale <- scale_y_continuous(limits = range(RTdata1$RT))
RTdata2 <- df.C1.V.sum_rt_acc_l %>%
  select(Subject,Task,Morality,Identity,RT) %>% 
  filter(Task == "Id"& Morality == 'Bad')
RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  guides(fill = FALSE) +guides(color = FALSE)+
  theme_bw() +
  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")

setwd(traDir)
tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
p_rt_match <- multiplot(p1,p2,cols = 2)
dev.off()
setwd(curDir)
multiplot(p1,p2,cols = 2)
```

>>>>

# exclude participant (1st round)
excldSub1_M  <- c()     # subject ID of those who failed matching task
excldSub1_C  <- c(7338) # subject 7338 excluded because Accuracy of one condition is zero

df.M1.trials <-  plyr::ddply(df.M1,.(Subject, Match, Identity,Morality), summarise,
                    N = length(ACC),
                    countN = sum(ACC))
subjlistM <- unique(df.M1.trials$Subject)

# exclude particiapnts (2nd round: incorrect trial number)
excldSub2_M <- c()
for (ii in 1:length(subjlistM)){
  tmp <- subset(df.M1.trials,Subject == subjlistM[ii])
  if(sum(tmp$N != 75)){ # if the number of trials in matching task correct 
    excldSub2_M[ii] <- subjlistM[ii]
    print(paste0("ERROR: the trials number of subject ", subjlistM[ii] , 
                 " in matching task is not correct"))
}}

@@

# exclude participants (3rd round: < 0.5 overall accuracy)
df.M1.acc.g <-  plyr::ddply(df.M1,.(Subject), summarise,
                    N = length(ACC),
                    countN = sum(ACC),
                    ACC = sum(ACC)/length(ACC))

@@

# all participants excluded
excldSub_M   <- c(excldSub1_M, excldSub2_M,excldSub3_M)
excldSub_M <- excldSub_M[!duplicated(excldSub_M)]   # total excluded for matching task

@@

# particiapnts with valid data
valdSub_M <- setdiff(subjlistM, excldSub_M)
valdSub_C <- setdiff(subjlistC, excldSub_C)

# select valid data for further analysis
df.M1.valid <- df.M1[!(df.M1$Subject %in% excldSub_M),]   # exclude the invalid subjects
df.C1.valid <- df.C1[!(df.C1$Subject %in% excldSub_C),]
# df.C1.valid <- df.C1.valid[!(df.C1.valid$Subject %in% excld.sub.T),]

@@

# get the data file for hddm analysis
df.M.ddm.v <- df.M[!(df.M$Subject %in% excldSub_M),]   # exclude the invalid subjects
df.C.ddm.v <- df.C[!(df.C$Subject %in% excldSub_C),]

@@

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
#RTdata1 <- df.M1.V.sum_rt_acc_l %>%
#  select(Subject,Match,Morality,Identity,RT) %>% 
#  filter(Match == "match" & Morality == "Good")
#RTdata1$Identity <- factor(RTdata1$Identity,levels = c("Self","Other"))
#p1 <- ggplot(data = RTdata1, aes(y = RT, x = Identity,fill = Identity)) +
#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
#  guides(fill = FALSE) +guides(color = FALSE)+
#  theme_bw() +
#  raincloud_theme+scale_y_continuous(limits = c(300,900))+labs(x = "Good",y = "Reaction times(ms)")
#RTdata2 <- df.M1.V.sum_rt_acc_l %>%
#  select(Subject,Match,Morality,Identity,RT) %>% 
#  filter(Match == "match" & Morality == "Bad")
#RTdata2$Identity <- factor(RTdata2$Identity,levels = c("Self","Other"))
#p2 <- ggplot(data = RTdata2, aes(y = RT, x = Identity,fill = Identity)) +
#  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
#  geom_point(aes(y = RT,color = Identity), position = position_jitter(width = .15), size = .5) +
#  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
#  guides(fill = FALSE) +guides(color = FALSE)+
#  theme_bw() +
#  raincloud_theme+scale_y_continuous(limits = c(300,900),breaks = NULL)+labs(x = "Bad",y = "")

#setwd(traDir)
#tiff("p_rt_match.tiff", width = 9, height = 6, units = 'in', res = 300)
#p_rt_match <- multiplot(p1,p2,cols = 2)
#dev.off()
#setwd(curDir)
#multiplot(p1,p2,cols = 2)
```

```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
```

```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)

```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
```

```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'RT', inData = df.C1.V.sum_rt_acc_l)

```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
```
